A Comparative Ecophysiological Survey of Lycophytes, Ferns, and Seed Plants

### 2019-03-01 manuscript/manuscript.Rmd
ratio stats

Light response curves were conducted by decreasing the light intensity in the gas exchange cuvette in small step changes. For each light response curve, The CO~2~ in the leaf cuvette was set to a flow rate of 300 $\mu$mol s^-1^ and at ambient atmospheric [CO~2~] (400 ppm). Initial light measurements were made using the built-in quantum sensor to determine typical ambient light levels. These measurements were used to generate light response curves using appropriate light levels for high-light and low-light species separately. The light levels were not identical for each species, with several points being added or subtracted with each run. Broadly, light response curves followed the same template for high light or low light species. For high light species, light levels started at a PPFD of 1500 $\mu$mol m^-1^ s^-1^ and then consisted of 16 additional steps to O $\mu$mol m^-1^ s^-1^. For low light species, light response curves started at a PPFD of 500 $\mu$mol m^-1^ s^-1^, followed by 13 additional steps to O $\mu$mol m^-1^ s^-1^. Light response data for each curves was fit to a non-rectangular hyperbola model (Equation 6 in Lobo et al. 2013). The light compensation point (LCP) was calculated as the PPFD at which the net photosynthetic rate equalled zero from the linear phase of each light response curve. Quantum yeild ($\phi$) was calculated as the initial slope of the assimilation rate and mitochondrial respiration in the light (R~d~) at the step change where PPFD was 0 $\mu$mol m^-1^ s^-1^.

@@

temperature?

@@

@@

In open canopy environments, ferns had significantly lower phosphorus concentrations than those growing in closed canopies. Angiosperms had no significant difference across the light gradient. In both environments, ferns and lycophytes do not differ significantly, but both have significantly lower phosphorus levels than angiosperms (Figure asdf). Ferns in open light environments have significantly lower nitrogen levels than those ferns growing in closed light environments; the same is true of angiosperms. Lycophytes have significantly lower nitrogen levels than ferns and angiosperms, which do not statistically differ, in both light conditions (Figure adf).

>>>>

Light response curves were conducted by decreasing the light intensity in the gas exchange cuvette in small step changes. For each light response curve, The CO~2~ in the leaf cuvette was set to a flow rate of 300 $\mu$mol s^-1^ and at ambient atmospheric [CO~2~] (400 ppm). Temperature was not explictly controlled in the leaf cuvette and leaf temperatures ranged from 27-30 &deg;C. Initial light measurements were made using the built-in quantum sensor to determine typical ambient light levels. These measurements were used to generate light response curves using appropriate light levels for high-light and low-light species separately. The light levels were not identical for each species, with several points being added or subtracted with each run. Broadly, light response curves followed the same template for high light or low light species. For high light species, light levels started at a PPFD of 1500 $\mu$mol m^-1^ s^-1^ and then consisted of 16 additional steps to O $\mu$mol m^-1^ s^-1^. For low light species, light response curves started at a PPFD of 500 $\mu$mol m^-1^ s^-1^, followed by 13 additional steps to O $\mu$mol m^-1^ s^-1^. Light response data for each curves was fit to a non-rectangular hyperbola model (Equation 6 in Lobo et al. 2013). The light compensation point (LCP) was calculated as the PPFD at which the net photosynthetic rate equalled zero from the linear phase of each light response curve. Quantum yeild ($\phi$) was calculated as the initial slope of the assimilation rate and mitochondrial respiration in the light (R~d~) at the step change where PPFD was 0 $\mu$mol m^-1^ s^-1^.

@@

@@

add vegan

@@

In open canopy environments, ferns had significantly lower phosphorus concentrations than those growing in closed canopies. Angiosperms had no significant difference across the light gradient. In both environments, ferns and lycophytes do not differ significantly, but both have significantly lower phosphorus levels than angiosperms (Figure asdf). Ferns in open light environments have significantly lower nitrogen levels than those ferns growing in closed light environments; the same is true of angiosperms.

Across closed canopy habitats, Lycophytes have 45% lower foliar nitrogen levels than ferns and angiosperms, which do not statistically differ (*P* < 0.001). Conseqently, Lycpohtes had significantly higher CN ratios than ferns and angiosperms (*P* < 0.001). No differences were detected  between Lycophytes, ferns and angiosperms across closed canopy habitats.
